\documentclass[12pt]{article}

\usepackage{parskip}
\usepackage[margin=1in]{geometry}

\begin{document}
\pagestyle{empty}
\setlength{\parindent}{10cm}

\begin{center}
\begin{huge}\textbf{Jason Fang}\end{huge}\\
\rule{475pt}{1pt}
\textbf{159 University Avenue West $\cdot$ 519.501.6528 $\cdot$ jason.fang.1@uwaterloo.ca} 
\end{center}


\setlength{\parindent}{0pt}

\vspace{24pt}January 20th, 2014 

Alcatel-Lucent Inc.

Dear Recruiter,

\paragraph*{}\hspace{10pt}As an aspiring software engineer, I hope you will consider me for the position of software designer, as advertised on JobMine.

\paragraph*{}\hspace{10pt}This job caught my eye because I've always preferred to design software as opposed to implementing it, since it allows me to utilize my creative skills to make original, new, and efficient software. My passion is programming, and so I am very self-motivated when it comes to learning programming. Over the summer I've taught myself a lot of new skills that I was interested in, such as Linux OS Development, command line, Android, and \LaTeX. I embody many of the characteristics that you look for in the ideal candidate. I have 2 years of experience developing object orientated programs in Java and therefore understand a lot of the concepts attached to it. In addition, I am accustomed to the fast-paced environment of many software companies in this age as I have a year of experience developing apps for clients in an agile environment. 

\paragraph*{}\hspace{10pt}All my side projects can be found in my GitHub repository under https://github.com/jasonf7 for reference. Attached to the cover letter you will find my resume which showcases all of the skills I posses that I will bring to your company.

\paragraph*{}\hspace{10pt}Thank you for taking the time to consider me for the position. I look forward to hearing back from you.

\vspace{12pt}Sincerely,

\vspace{12pt}Jason Fang

\end{document}